The Controlled Choice Design and Paternalism in Pawnshop Borrowing? \\ Preliminary --comments welcome

### 2023-04-20 OA.tex
changes after presentation(s)...rewriting of text

\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
    \end{center}
     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
\end{figure}

>>>>

\begin{figure}[H]
        \caption{Financial cost TUT effect for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
     \scriptsize This Figure estimates the treatment effect on financial cost for the untreated with different discount rates.  
     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
\end{figure}

\begin{figure}[H]
    \caption{Partitoin of TuT \& ToT effect by behavioral variables.}
    \label{tut_beh_partition}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{TuT}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tut_beh_partition.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{ToT}
        \centering
        \includegraphics[width=\textwidth]{Figuras/tot_beh_partition.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize    \\
      %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
\end{figure}

### 2023-04-20 Tables/decomposition_main_te_pres1.tex
changes after presentation(s)...rewriting of text

% Table generated by Excel2LaTeX from sheet 'decomposition_main_te_pres1'
\begin{tabular}{lcccccc}
\toprule
      &       & \multicolumn{5}{c}{Components of FC} \\
\cmidrule{3-7}      & FC    & \textcolor[rgb]{ .749,  .749,  .749}{Int. pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Fee pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Princ. pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Lost pawn val} & Default \\
\midrule
      & (1)   & \textcolor[rgb]{ .749,  .749,  .749}{(2)} & \textcolor[rgb]{ .749,  .749,  .749}{(3)} & \textcolor[rgb]{ .749,  .749,  .749}{(4)} & \textcolor[rgb]{ .749,  .749,  .749}{(5)} & (6) \\
\midrule
\midrule
Forced cmit & \boxit{0.5in} -379.7*** & \textcolor[rgb]{ .749,  .749,  .749}{-157.3***} & \textcolor[rgb]{ .749,  .749,  .749}{32.1***} & \textcolor[rgb]{ .749,  .749,  .749}{-0.57} & \textcolor[rgb]{ .749,  .749,  .749}{-254.5**} & \boxit{0.5in} -0.065*** \\
      & (111.4) & \textcolor[rgb]{ .749,  .749,  .749}{(34.9)} & \textcolor[rgb]{ .749,  .749,  .749}{(1.43)} & \textcolor[rgb]{ .749,  .749,  .749}{(3.03)} & \textcolor[rgb]{ .749,  .749,  .749}{(104.8)} & (0.023) \\
Choice cmit & -84.9 & \textcolor[rgb]{ .749,  .749,  .749}{-24.9} & \textcolor[rgb]{ .749,  .749,  .749}{1.34**} & \textcolor[rgb]{ .749,  .749,  .749}{-3.98} & \textcolor[rgb]{ .749,  .749,  .749}{-61.4} & -0.025 \\
      & (114.6) & \textcolor[rgb]{ .749,  .749,  .749}{(38.4)} & \textcolor[rgb]{ .749,  .749,  .749}{(0.54)} & \textcolor[rgb]{ .749,  .749,  .749}{(2.47)} & \textcolor[rgb]{ .749,  .749,  .749}{(109.2)} & (0.021) \\
      &       & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} &  \\
\midrule
Observations & 6304  & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & 6304 \\
R-squared & 0.007 & \textcolor[rgb]{ .749,  .749,  .749}{0.022} & \textcolor[rgb]{ .749,  .749,  .749}{0.151} & \textcolor[rgb]{ .749,  .749,  .749}{0.003} & \textcolor[rgb]{ .749,  .749,  .749}{0.007} & 0.013 \\
Control Mean & 1851.0 & \textcolor[rgb]{ .749,  .749,  .749}{545.9} & \textcolor[rgb]{ .749,  .749,  .749}{0} & \textcolor[rgb]{ .749,  .749,  .749}{5.82} & \textcolor[rgb]{ .749,  .749,  .749}{1305.1} & 0.44 \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'decomposition_main_te_pres1'
\begin{tabular}{lcccccccc}
\toprule
      &       & \multicolumn{5}{c}{Components of FC}  &       &  \\
\cmidrule{3-7}      & FC    & \textcolor[rgb]{ .749,  .749,  .749}{Int. pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Fee pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Princ. pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Lost pawn val} & Default &       & APR \\
\midrule
      & (1)   & \textcolor[rgb]{ .749,  .749,  .749}{(2)} & \textcolor[rgb]{ .749,  .749,  .749}{(3)} & \textcolor[rgb]{ .749,  .749,  .749}{(4)} & \textcolor[rgb]{ .749,  .749,  .749}{(5)} & (6)   &       & (7) \\
\midrule
\midrule
Forced cmit & \boxit{0.35in} -379.7*** & \textcolor[rgb]{ .749,  .749,  .749}{-157.3***} & \textcolor[rgb]{ .749,  .749,  .749}{32.1***} & \textcolor[rgb]{ .749,  .749,  .749}{-0.57} & \textcolor[rgb]{ .749,  .749,  .749}{-254.5**} & \boxit{0.35in} -0.065*** &       & \boxit{0.35in} -0.34*** \\
      & (111.4) & \textcolor[rgb]{ .749,  .749,  .749}{(34.9)} & \textcolor[rgb]{ .749,  .749,  .749}{(1.43)} & \textcolor[rgb]{ .749,  .749,  .749}{(3.03)} & \textcolor[rgb]{ .749,  .749,  .749}{(104.8)} & (0.023) &       & (0.080) \\
Choice cmit & -84.9 & \textcolor[rgb]{ .749,  .749,  .749}{-24.9} & \textcolor[rgb]{ .749,  .749,  .749}{1.34**} & \textcolor[rgb]{ .749,  .749,  .749}{-3.98} & \textcolor[rgb]{ .749,  .749,  .749}{-61.4} & -0.025 &       & -0.12 \\
      & (114.6) & \textcolor[rgb]{ .749,  .749,  .749}{(38.4)} & \textcolor[rgb]{ .749,  .749,  .749}{(0.54)} & \textcolor[rgb]{ .749,  .749,  .749}{(2.47)} & \textcolor[rgb]{ .749,  .749,  .749}{(109.2)} & (0.021) &       & (0.073) \\
      &       & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} &       &       &  \\
\midrule
Observations & 6304  & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & 6304  &       & 6304 \\
R-squared & 0.007 & \textcolor[rgb]{ .749,  .749,  .749}{0.022} & \textcolor[rgb]{ .749,  .749,  .749}{0.151} & \textcolor[rgb]{ .749,  .749,  .749}{0.003} & \textcolor[rgb]{ .749,  .749,  .749}{0.007} & 0.013 &       & 0.011 \\
Control Mean & 1851.0 & \textcolor[rgb]{ .749,  .749,  .749}{545.9} & \textcolor[rgb]{ .749,  .749,  .749}{0} & \textcolor[rgb]{ .749,  .749,  .749}{5.82} & \textcolor[rgb]{ .749,  .749,  .749}{1305.1} & 0.44  &       & 1.84 \\
\bottomrule
\bottomrule
\end{tabular}%
